\documentclass{f4_beamer_metropolis}

\title{TLS v1.3}
\subtitle{SITS WS18/19}
\author{Dennis Grabowski, B.Sc}
\date{28.11.2018}

\begin{document}

% Cannot be moved into the class
\begin{frame}{Table of contents}
    \tableofcontents[hideallsubsections]
  \end{frame}

\section{Motivation}

\begin{frame}{TLS 1.2}
\begin{itemize}
  \item TLS 1.2 release was 10 years ago
  \item Last change to specification: RFC 6176 in 2011
\end{itemize}
\end{frame}

\begin{frame}{What new, relevant technologies were invented?}
  \begin{itemize}
    \item
  \end{itemize}
  \end{frame}

\begin{frame}{What new attacks were discovered?}
  \begin{itemize}
    \item
  \end{itemize}
\end{frame}

\section{Changes to the current protocol}

\subsection{1-RTT Handshake instead 2-RTT}

\begin{frame}{TLS v1.2 Handshake}
How does the TLS 1.2 Handshake work currently?
\end{frame}

\begin{frame}{}[standout]
  TLS v1.2 Handshake - Wiresharkdemo
\end{frame}

\begin{frame}{TLS v1.3 Handshake}
  How does the TLS 1.3 Handshake work?
  Where exactly are the changes?
\end{frame}

\begin{frame}{}[standout]
  TLS v1.3 Handshake - Wiresharkdemo
\end{frame}

\section{New Features coming to TLS 1.3}

\subsection{0-RTT Resumption}

\begin{frame}{}

\end{frame}

\subsection{Protection from downgrading}

\begin{frame}{What is downgrading?}

\end{frame}

\section{Features removed from TLS 1.3}

\subsection{Why do features need to be removed?}

\begin{frame}{}

\end{frame}

\subsection{Removed Cipher Suites, Hashing Functions...}

\begin{frame}{}

\end{frame}

\subsection{Compression}

\begin{frame}{}

\end{frame}

\subsection{Renegotiation}

\begin{frame}{}

\end{frame}

\section{Conclusion}

\begin{frame}{}

\end{frame}

\begin{frame}[standout]
  Questions?
\end{frame}

\end{document}
